RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-04-27 manuscripts/manuscript.Rmd

The `RNeXML` interface described above for built-in metadata allows
users to create precise and semantically rich annotations without 
confronting any of the complexity of namespaces and ontologies.
Nevertheless, advanced users may desire the explicit control over
these semantic tools to take full advantage of the flexibility
and extensibility of the NeXML specification [@Vos2012; @Parr2011].
In this section we detail how to accomplish these more complex uses
in RNeXML.

>>>>

The `RNeXML` interface described above for built-in metadata allows
users to create precise and semantically rich annotations without 
confronting any of the complexity of namespaces and ontologies.
Nevertheless, advanced users may desire the explicit control over
these semantic tools that takes full advantage of the flexibility
and extensibility of the NeXML specification [@Vos_2012; @Parr2011].
In this section we detail how to accomplish these more complex uses
in RNeXML.
